
   %%%%%%%%%%%%%%%%%%%%%%%
 %%%  NOAH'S SUPER COOL  %%%
%%%%      ACADEMIC       %%%%
 %%%   LATEX TEMPLATE    %%%
   %%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt]{article}
\usepackage[letterpaper]{geometry}
\geometry{top=1in, bottom=1in, left=1in, right=1in}
\usepackage{fontspec}
\usepackage{tgtermes}
\usepackage{hanging}
\setmainfont[
 ItalicFont={texgyretermes-italic.otf},
 BoldFont={texgyretermes-bold.otf},
 ]{texgyretermes-regular.otf}
\usepackage{setspace}
\doublespacing
\usepackage{enumitem}
\setenumerate[1]{label=\Roman*.}
\setenumerate[2]{label=\Alph*.}
\setenumerate[3]{label=\roman*.}
\setenumerate[4]{label=\alph*.}
\begin{document}

\pagenumbering{gobble}
\begin{center}
\topskip0pt
\vspace*{\fill}

\textbf{For Milwaukee School of Engineering Young Democratic Socialists of America} \\
\textbf{endorsing Wisconsin gubernatorial candidate Francesca Hong} \\
- \\
Noah Dinan \\
\today \\

\vspace*{\fill}
\end{center}

\newpage

\onehalfspacing

\begin{center}
For MSOE YDSA endorsing Francesca Hong
\end{center}

\setlength{\parindent}{0in}



\textbf{Whereas,} members of MSOE's YDSA and the greater Wisconsin community will
benefit from Francesca Hong's leadership and policies. \\

\textbf{Whereas,} Hong's campaign focuses on affordability for working class people while de-emphasizing
the wealthy ruling class and their abuse of power. \\

\textbf{Whereas,} Hong's campaign demands safety, freedom, and economic security for all people. \\

\textbf{Whereas,} Hong's campaign will be fully funded by donations and not bribed by wealthy corporations
and therefore requires effective fundraising. \\

\textbf{Whereas,} Hong's campaign holds the following goals

\begin{itemize}
    \item Affordable living for all
    \item Universal childcare
    \item Expand BadgerCare access
    \item Guaranteed abortion access, reproductive freedom, and gender affirming care
    \item Protections for LGBTQ+, immigrant, and other oppressed groups
    \item Stop systematically funding billionaires and wealthy corporations
    \item Empower small businesses \\
\end{itemize}

\newpage

\textbf{Therefore be it resolved,} the Milwaukee School of Engineering YDSA will
formally endorse gubernatorial candidate Francesca Hong in her race for Governor of Wisconsin. \\

\textbf{Resolved,} the MSOE YDSA will endorse candidate Francesca Hong on social media platforms. \\

\textbf{Resolved,} the MSOE YDSA will hold at least three tabling events promoting
candidate Francesca Hong on campus. \\

\textbf{Resolved,} the MSOE YDSA will hold at least 2 community events promoting
candidate Francesca Hong in the Milwaukee community. \\

\textbf{Resolved,} the MSOE YDSA will hold an email fundraising campaign for Francesca Hong's
campaign preceding August 2026. \\

\textbf{Resolved,} the MSOE YDSA will hold an email fundraising campaign for Francesca Hong's
campaign between August 2026 and November 3rd, 2026.

\end{document}
