\documentclass[12pt]{article}

% Margin - 1 inch on all sides
\usepackage[letterpaper]{geometry}
\geometry{top=1.1in, bottom=1.1in, left=1.1in, right=1.1in}

\usepackage{fontspec}
\usepackage{tgtermes}
\usepackage{hanging}

\setmainfont[
 ItalicFont={texgyretermes-italic.otf},
 ]{texgyretermes-regular.otf}


% Doublespacing
\usepackage{setspace}
\doublespacing

% Outline stuffs
\usepackage{outlines}
\usepackage{enumitem}

\setenumerate[1]{label=\Roman*.}
\setenumerate[2]{label=\Alph*.}
\setenumerate[3]{label=\roman*.}
\setenumerate[4]{label=\alph*.}

% Begin document
\begin{document}

% Title
\begin{center}
Outline
\end{center}

\begin{outline}[enumerate]
\1 Introduction
    \2 Thesis: diverse perspectives are detrimental to the success of propaganda

\1 Power of the television for propaganda
    \2 Vermes' Hitler character is upset that there is more than only one channel on the TV.
    \2 quote on pg. 63

\1 Adichie connection
    \2 A single story (single perspective) provides power to propaganda
    \2 quote on hitler's single story perspective

\1 Snyder connection
    \2 discussion of avoiding propaganda and connect to single perspective.
    \2 tyrants and being cautious to propaganda
    \2 example of hitler's of tyranny

\1 Academic source outside of class 
    \2 Vermes connection

\1 Academic source outside of class 
    \2 Vermes connection

\1 Conclusion

\end{outline}

\newpage

% First page name, class, etc
\noindent
Noah Dinan \\ Mark Zimmermann \\ COM1001 \\ \today \\

% Title
\begin{center}
Research Essay
\end{center}

% Indentation
\setlength{\parindent}{0.5in}

Essay essay...\\

Essay!!

% Bibliography
\newpage

\begin{center}
Works Cited
\end{center}

\begin{hangparas}{0.5in}{1}

“Gantry Crane: What Is It? How Is It Used? Types, Classes.” Gantry Crane, Industrial Quick Search,
https://www.iqsdirectory.com/articles/crane/gantry-cranes.html. Accessed 05 Nov. 2024. 

\end{hangparas}
\end{document}
