
   %%%%%%%%%%%%%%%%%%%%%%%
 %%%%  FREE PALESTINE  %%%%
   %%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}
\usepackage[letterpaper]{geometry}
\geometry{top=1in, bottom=1in, left=1in, right=1in}
\usepackage{fontspec}
\usepackage{tgtermes}
\usepackage{hanging}
\setmainfont[
 ItalicFont={texgyretermes-italic.otf},
 BoldFont={texgyretermes-bold.otf},
 ]{texgyretermes-regular.otf}
\usepackage{setspace}
\singlespacing
\usepackage{outlines}
\usepackage{enumitem}
\setenumerate[1]{label=\Roman*.}
\setenumerate[2]{label=\Alph*.}
\setenumerate[3]{label=\roman*.}
\setenumerate[4]{label=\alph*.}
\begin{document}

% Title Page
\pagenumbering{gobble}

\begin{center}
\textbf{Testimony Against AB446}
\end{center}

\setlength{\parindent}{0in}

Noah Dinan on the behalf of
Calais Chmielewski, Emily Claire Lorenzen, Conor Mika, Avery O’Shaughnessy, Cameron Konicek, Daniel Peter Portwine, Daisy DiCarlo, Quinn Gordon \\

My name is Noah Dinan, I am a student at Milwaukee School of Engineering, and I condemn hate speech and violence. \\

While at a community event in Milwaukee, I was told of the proposed bill AB446 and its negative impacts on the people of Wisconsin.
This bill will allow courts to infringe on citizens’ freedoms of speech and assembly, because those who have committed trivial 
infractions in the past may be penalized with an additional hate crime charge for speaking out against Israel. \\

The IHRA’s definition of antisemitism states that manifestations of antisemitism might appear as targeting the state of Israel,
but that criticisms of Israel in the same spirit as criticisms of any other country should not be included.
This is a dangerously vague definition, and I believe this vagueness will be leveraged against peaceful, pro-Palestinian groups
that protest Israel’s war crimes and ongoing genocide in the Gaza Strip and West Bank.
The executive director of Jewish Voice for Peace stated,

\begin{center}
“We’re enormously proud to stand with over 30 Jewish organizations worldwide to say no to this harmful definition of antisemitism
and yes to human rights and the freedom to protest” (Vilkomerson). 
\end{center}

Even the IHRA creators of this definition are opposed to its use in legislation. The definition is clearly preceded by the statement
that it is to be used as a non-legally binding working definition. \\

Bill AB446 states that it does not intend to infringe on any first amendment rights, but I implore you to consider the timing of this
bill’s proposal. It did not come in 2016, when the International Holocaust Remembrance Alliance’s definition of antisemitism was first created.
It did not come any time in the past two years as we watched the despicable surge of antisemitism in the United States.
It did come now, as pressures against Israel are at an all-time high. I do not believe that this bill has to do with curbing antisemitism.
I believe it has everything to do with silencing opposition to the state of Israel. \\

You stand at this moment with a choice between free speech or censorship. As a voting citizen from Milwaukee,
a constituent of members of this governing body and representing several others, I demand that you oppose bill AB446.
Protect Wisconsin's first amendment rights; do not allow the criticism of Israel to become illegal,
just as the criticism of any other country is not. Any member of this body who votes yes to this bill will lose my vote in upcoming elections,
as well as the votes of countless members of my community. \\

Thank you.

\vspace*{\fill}

\begin{center}
“\textbf{Adopt the following non-legally binding working definition of antisemitism:}

Antisemitism is a certain perception of Jews, which may be expressed as hatred toward Jews. Rhetorical and physical manifestations of antisemitism are directed toward Jewish or non-Jewish individuals and/or their property, toward Jewish community institutions and religious facilities” 

(IHRA non-legally binding working definition of antisemitism, May 2016). 
\end{center}

\end{document}
