
   %%%%%%%%%%%%%%%%%%%%%%%
 %%%  NOAH'S SUPER COOL  %%%
%%%%      ACADEMIC       %%%%
 %%%   LATEX TEMPLATE    %%%
   %%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt]{article}
\usepackage[letterpaper]{geometry}
\geometry{top=1in, bottom=1in, left=1in, right=1in}
\usepackage{amsmath}
\usepackage{fontspec}
\usepackage{tgtermes}
\usepackage{hanging}
\usepackage{gensymb}
\setmainfont[
 ItalicFont={texgyretermes-italic.otf},
 BoldFont={texgyretermes-bold.otf},
 ]{texgyretermes-regular.otf}
\usepackage{setspace}
\doublespacing
\usepackage{graphicx}
\graphicspath{ {./graphics/} }

\begin{document}

% Title Page
\pagenumbering{gobble} % remove page numbers
\begin{center}
\topskip0pt
\vspace*{\fill}
Measuring the Speed of Sound \\ Lab 13 - Noah Dinan \\ PHY 1110 - Mayer \\ \today \\
\vspace*{\fill}
\end{center}

\newpage
\pagenumbering{arabic} % resume page numbering
\setlength{\parindent}{0in}

\textbf{Results}\vspace{1em}

A sound wave is a pressure wave that moves through the air. This wave has a speed
that can be measured. The speed of any wave is $v = f\lambda$ where $f$ is the frequency
and $\lambda$ is the wavelangth.

We can use an ultrasonic transmitter + reciever system in order to generate sound waves at 40,000 Hz.

Our measurement of wavelength has an uncertainty of $\pm$ 0.1 based on the scale used.

To determine wavelength, we counted the number of waves and distance.

\[ \lambda = \frac{\text{distance}}{\text{\# of waves}} \]

\[ \lambda = 1.02 \pm 0.1 \text{cm} \]

This allows us to determine the speed of sound.

\[ v = [40000][0.0102] \]

\[ v = 408 \pm \text{40 meters per second}\]

Potential sources of experimental error could have come from measuring the distance for the wave,
although averaging 50 waves will certainly reduce this error. Another potential source of error comes from
an inability to set the function generator to exactly 40k Hz.

\newpage

\textbf{Conclusions}\vspace{1em}

The expected value for the speed of sound at room temperature (20$\degree$ Celsius) is 343 meters per second.

Comparing our found speed of sound (408 $\pm$ 40) to the book value shows that we were fairly accurate.
Differences in temperature may have impacted the change in addition to possible
experimental error.

\end{document}
